Air cargo load and route planning in pickup and delivery operations

### 2024-01-27 latex/eswa.tex
Included a map of Brazil

To validate the effectiveness of the {\it Shims} heuristic, we solve a 15-node TSP containing the 15 main Brazilian airports.
For this task, we implemented a TSP solution method based on the Genetic Algorithm (GA) that returns the 20\% best tours as input to the ACLP-RPDP solved by {\it Shims}.

@@

DEAP took 3 seconds to solve a 15-node TSP.

@@

>>>>

To validate the effectiveness of the {\it Shims} heuristic, we solve a 15-node TSP containing the 15 main Brazilian airports.
For this task, we implemented a TSP solution method based on the Genetic Algorithm (GA) that returns a population of 100 tours as input to the ACLP-RPDP solved by {\it Shims}. The GA run time was around three seconds, and the total run time was around 33 seconds.

@@

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{brazil.png}
	\caption{ {\it Shims/GA} best tour (may not be optimal)}
	\label{fig:brazil}
\end{figure}
}
